A pipeline to analyse time-course gene expression data

### 2019-08-30 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

\textbf{EAP: We need to add comment about microarray versus sequencing data}

@@

@@

\begin{tabular}{lllrrrlr}
\toprule
  & GO ID & Description & Annotated & Significant & Expected & P-value & adj. p-value\\
\midrule
5 & GO:0003002 & regionalization & 172 & 153 & 134.41 & 0.00026 & 0.2629\\
6 & GO:0048562 & embryonic organ morphogenesis & 152 & 135 & 118.78 & 0.00045 & 0.3323\\
7 & GO:0010970 & transport along microtubule & 82 & 75 & 64.08 & 0.00046 & 0.3323\\
8 & GO:0006805 & xenobiotic metabolic process & 49 & 47 & 38.29 & 0.00059 & 0.3729\\
9 & GO:0060173 & limb development & 92 & 84 & 71.89 & 0.00068 & 0.3820\\
\addlinespace
10 & GO:0019395 & fatty acid oxidation & 53 & 51 & 41.42 & 0.00134 & 0.6194\\
11 & GO:0055114 & oxidation-reduction process & 536 & 461 & 418.84 & 0.00139 & 0.6194\\
12 & GO:0060070 & canonical Wnt signaling pathway & 149 & 131 & 116.43 & 0.00147 & 0.6194\\
13 & GO:0090596 & sensory organ morphogenesis & 134 & 118 & 104.71 & 0.00219 & 0.8517\\
14 & GO:0060411 & cardiac septum morphogenesis & 33 & 32 & 25.79 & 0.00295 & 1.0000\\
\addlinespace
15 & GO:0010811 & positive regulation of cell-substrate ad... & 81 & 73 & 63.30 & 0.00384 & 1.0000\\
16 & GO:0042738 & exogenous drug catabolic process & 22 & 22 & 17.19 & 0.00437 & 1.0000\\
17 & GO:1901381 & positive regulation of potassium ion tra... & 22 & 22 & 17.19 & 0.00437 & 1.0000\\
18 & GO:0007368 & determination of left/right symmetry & 66 & 60 & 51.57 & 0.00536 & 1.0000\\
19 & GO:0060078 & regulation of postsynaptic membrane pote... & 66 & 60 & 51.57 & 0.00536 & 1.0000\\
\bottomrule
\end{tabular}

\hypertarget{session-information}{%
\section{Session information}\label{session-information}}

@@

>>>>

@@

While we showcase this pipeline on micro-array data, \citep{varoquaux:lifecycle}
leverages a similar set of steps to analyse RNA-seq data of the lifetime
transcriptomic response of the crop \emph{S. bicolor} to drought.

@@

\begin{tabular}{llrrrlr}
\toprule
GO ID & Description & Annotated & Significant & Expected & P-value & Adj. p-value\\
\midrule
GO:0003002 & regionalization & 172 & 153 & 134.41 & 0.00026 & 0.263\\
GO:0048562 & embryonic organ morphogenesis & 152 & 135 & 118.78 & 0.00045 & 0.332\\
GO:0010970 & transport along microtubule & 82 & 75 & 64.08 & 0.00046 & 0.332\\
GO:0006805 & xenobiotic metabolic process & 49 & 47 & 38.29 & 0.00059 & 0.373\\
GO:0060173 & limb development & 92 & 84 & 71.89 & 0.00068 & 0.382\\
\addlinespace
GO:0019395 & fatty acid oxidation & 53 & 51 & 41.42 & 0.00134 & 0.619\\
GO:0055114 & oxidation-reduction process & 536 & 461 & 418.84 & 0.00139 & 0.619\\
GO:0060070 & canonical Wnt signaling pathway & 149 & 131 & 116.43 & 0.00147 & 0.619\\
GO:0090596 & sensory organ morphogenesis & 134 & 118 & 104.71 & 0.00219 & 0.852\\
GO:0060411 & cardiac septum morphogenesis & 33 & 32 & 25.79 & 0.00295 & 1.000\\
\addlinespace
GO:0010811 & positive regulation of cell-substrate ad... & 81 & 73 & 63.30 & 0.00384 & 1.000\\
GO:0042738 & exogenous drug catabolic process & 22 & 22 & 17.19 & 0.00437 & 1.000\\
GO:1901381 & positive regulation of potassium ion tra... & 22 & 22 & 17.19 & 0.00437 & 1.000\\
GO:0007368 & determination of left/right symmetry & 66 & 60 & 51.57 & 0.00536 & 1.000\\
GO:0060078 & regulation of postsynaptic membrane pote... & 66 & 60 & 51.57 & 0.00536 & 1.000\\
\bottomrule
\end{tabular}

The source code for this workflow can be found at
\url{https://github.com/NelleV/2019timecourse-rnaseq-pipeline}.
Archived source code at the time of publication can be foud at \url{XXX}.

All packages use in the workflow are available on GitHub, CRAN, or
Bioconductor.

Data used in this workflow are available from NCBI GEO, accession
\href{https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE63786}{GSE63786}.
Normalized data can be found in \texttt{moanin}. Normalization information is
provided as supplementary information.

Last but not least, we use \texttt{sessionInfo()} to display all packages used in
this pipeline and their version numbers.

@@

\hypertarget{software-and-data-availability-1}{%
\section{Software and data availability}\label{software-and-data-availability-1}}
